---
title: "Prepping for association studies"
output: html_notebook
---

Even though there is clearly an effect of sequencing platform (that actually
shows up on PC-1) between the Hi-Seq and the Nova-Seq data, we are going to
just do an exploratory GWAS or two.  We just need to prep some sample lists
and some dot-sample files.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

# there is one sample that is somehow in this twice so we
# filter it out:
meta <- read_csv("Chinook_merged_metadata.csv") %>%
  filter(!duplicated(vcf_name))

```

## CV vs all southern Hemi

Let's compare the non-winter-run CV to the NZ and Arg together:

```{r}
samples1 <- meta %>%
  filter(!str_detect(Population, "Trinity|Salmon")) %>%
  filter(run_type != "Winter") %>%
  select(vcf_name) %>%
  rename(ID = vcf_name)

tmp <- samples1 %>%
  mutate(hemi = as.character(ifelse(str_detect(ID, "^DP"), 0, 1)))  # hemisphere south = 1, north = 0

dotsample1 <- bind_rows(tibble(ID = "0", hemi = "B"), tmp)

write_lines(samples1$ID, file = "../sample_lists/cv-and-south-hemi.txt")
dir.create("../dot-samples", showWarnings = FALSE, recursive = TRUE)
write_tsv(dotsample1, file = "../dot-samples/cv-and-south-hemi.tsv")
```


Also, we want to get a sample list of only the NZ fish:
```{r}
NZ_only <- meta %>%
  filter(str_detect(vcf_name, "^T")) %>%
  filter(!(Population %in% c(
    "Rio de las Vueltas",
    "Rio De Las Vueltas",
    "Sacramento River",
    "Santa Cruz Rive"
  )))

NZ_only %>%
  pull(vcf_name) %>%
  cat(., sep = "\n", file = "../sample_lists/nz-only.txt")
```